---
title: "Comparison of results between FUA and TTWA"
output:
  html_notebook: default
  html_document: default
---

```{r setup}
knitr::opts_knit$set(root.dir = '../../')

```

```{r, echo = F}
source.file <- 'RCI functions.R' #path to source
source(source.file)
```


##  Introduction 

This is a sensitivity analysis looking at whether we obtain different results if
we used functional urban area (2016) instead of travel to work area (2011).

To avoid excess duplication, we concentrate on the results for poor residents 
as defined by IMD income deprivation (and thus only on results for England). 

##  Data

The functional urban area definition comes from the Urban Audit 2016 which allows
for consistent defintions of an urban area across countries. We have 46 FUAs in
England and Wales. 129 TTWAs have some areas that falls within any FUA boundaries.
In effect FUA are usually areas that are far larger than TTWAs.

For the purposes of computing inequality indicies, we assign LSOAs to FUA based 
on the location of their population weighted centroids. Otherwise all other 
calculations of the inequality indicies remain unchanged from the main paper.

##  Results

We find that poor residents were on average more likely to be concentrated around
a) urban centres, b) employment opportunities and c) common amenities in both 2001
and 2011. 

```{r}


```


