---
title: "Comparison of results between FUA and TTWA"
output:
  html_notebook: default
  html_document: default
---

```{r setup}
knitr::opts_knit$set(root.dir = '../../')

```

```{r, echo = F}
source.file <- 'RCI functions.R' #path to source
source(source.file)
```


##  Introduction 

This is a sensitivity analysis looking at whether we obtain different results if
we used functional urban area (2016) instead of travel to work area (2011).

To avoid excess duplication, we concentrate on the results for poor residents 
as defined by IMD income deprivation (and thus only on results for England). 

##  Data

https://ec.europa.eu/eurostat/statistics-explained/index.php/Archive:European_cities_%E2%80%93_the_EU-OECD_functional_urban_area_definition

http://www.oecd.org/regional/redefiningurbananewwaytomeasuremetropolitanareas.htm

The functional urban area (FUA) definition was created by the OECD and European commission and allows
for consistent defintions of an urban area across countries. FUAs consist of at 
least one core city with a population of over 50,000 and its surrounding commuting 
zones based on population density and commuter flow data. A Travel to Work Area
contains a population where 75% of those working in a area live in that area (and 75% living in a TTWA work there).

We have 46 FUAs in England and Wales. 129 TTWAs have some areas that falls within any FUA boundaries.
The average TTWA used in the main paper has 327,000 residents whilst the average FUA has 955,000.
In summary, FUA are usually areas that are larger than TTWAs and can include
several TTWAs within their boundaries.

For the purposes of computing inequality indicies, we assign LSOAs to FUA based 
on the location of their population weighted centroids. Otherwise all other 
calculations of the inequality indicies remain unchanged from the main paper.

```{r}
inequal.tab_ttwa <-
  read.csv('Working analysis files/Duncan index results table.csv')

inequal.tab_ttwa <-
  inequal.tab_ttwa %>% 
  filter(type == 'inc')

stargazer::stargazer(inequal.tab_ttwa, type = 'text')

```



##  Results

```{r load in results}
inequal.tab <-
  read.csv('Working analysis files/Duncan index results table for FUA (optional).csv') 

inequal.tab <-
  inequal.tab %>% 
  filter(type == 'inc')
```


We find that poor residents were on average more likely to be concentrated around
a) urban centres (RCI: 0.15 to 0.12), b) employment opportunities (0.21 to 0.17) 
and c) common amenities (0.21 to 0.18) in both 2001
and 2011. 

```{r}
stargazer::stargazer(inequal.tab, type = 'text')
```

There is a strong correlation between RCI change and RAE (0.77) and moderate between
RCI and RPA (0.54). Larger FUAs have experienced greater negative changes in 
RCI (-0.25), RPA (-0.50) and RAE (-0.28). We note that only the correlation between
change RPA and population is statistically sigificant ($p$ < 0.01) However, we 
have reason to believe the lack of statistical non-sigificance for other relationships
can be attributed to lack of statistical power (i.e. 37 FUAs compared to 149 TTWAs).

```{r}
inequal.tab %>% 
  dplyr::select(total.pop, 
                rcidiff,
                workdiff_exp,
                geodiff) %>%
  cor(use = 'pairwise.complete.obs',
      method = 'spearman') %>%
  round(2)
```

```{r}
cor.test(formula =  ~ rcidiff + total.pop, 
         data = inequal.tab,
         method = 'spearman') 
## Not sig (but lower power and variance)

cor.test(formula =  ~ workdiff_exp + total.pop, 
         data = inequal.tab,
         method = 'spearman') 
# sig

cor.test(formula =  ~ geodiff + total.pop, 
         data = inequal.tab,
         method = 'spearman') 
# N.S
```

Overall we find that the main results of the paper do not change if we use FUA
instead of TTWA. We find similar results using jobseekers instead of low income
residents.